XXXXX

### 2014-12-23 paper/paper 2/paper 2.tex
DL mappings

\newenvironment{DL}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}
	\textbf{DL:} \\

}{
  \end{tabular}
  \linebreak
}

@@

@@

>>>>

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
	\begin{center}
  \begin{tabular}{r l}

}{
  \end{tabular}
	\end{center}
}

@@

\section{Notes}

\begin{itemize}
	\item requirements / constraints mapped to DL
	\item requirements / constraints which cannot be mapped to DL
	\item syntactic sugar for some constraints
	\item complex constraints encompass complex constraints and simple constraints
	\item DL statements of complex constraints are created out of DL statements of composed constraints 
	\item define terminology for RDF constraints
\end{itemize}

@@

\section{Complex Constraints}

\subsection{Disjoint Classes}

\begin{DL}
Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
Alternative:\\
$Hologram \sqsubseteq \neg Human$
\end{DL}

\subsection{Minimum Qualified Cardinality Restrictions on Properties}

\begin{DL}
$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
\end{DL}
